---
title: "R markdown for Classifying student passing and failing from network measures"
author: "Adrienne Traxler & Jesper Bruun"
date: "9/3/2020"
output: github_document 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Summarize results here.

**Update 6/9:** Started with collecting data information (since I keep forgetting which variables to use). 

```{r packages, echo = FALSE, message = FALSE}
library(igraph)
```

## Summary of data

### Networks

After the network data has been cleaned and assigned node attributes (by `loadAllNetworks.r`), and centrality values are calculated (by `calculatePR_TE_H.r`), the igraph objects are stored in `data/PRTEH.RData`.

```{r, echo = FALSE}
load("data/PRTEH.RData")
```

That file includes: 

* `accPS`, `accCD`, and `accICS`: Accumulated network objects for each week for the problem solving, concept discussion, and in-class social network layers. 
* `accPS_PR`, etc.: The `accXX_Y`-named objects hold centrality calculations for each layer for PageRank, Target Entropy, Hide. For TE and Hide, these are lists of vectors (one per week). For PageRank, it's a list of lists (one per week), with the centrality values we want in the `vector` entry of the list.

As part of standardizing the networks, they all have the same number of nodes, `r vcount(accPS[[1]])`. 

```{r}
sapply(accPS, vcount)
sapply(accCD, vcount)
sapply(accICS, vcount)
```

### Node information

There are also data frames of node information (after `make_node_data_frames.Rmd`), in `data/centrality_data_frames.Rdata`. This has:

* `dfPS`, `dfCD`, `dfICS`: A data frame for each layer listing week, node name, all predictor variables, and pass/justpass outcomes. 
* `nPass` and `nJustPass`: Tables of pass/fail counts (coded 1/0), for everyone and for people who were right on the border. For `nJustPass`, people not on the border are coded `NA`. 

```{r}
load("data/centrality_data_frames.Rdata")
nPass
nJustPass
```

## Logisitic regression results

