---
title: "Logistic regression"
author: "Jesper Bruun & Adrienne Traxler"
date: "3/30/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Goal for this document is to make exploratory plots and run logistic regression for passing and failing in the (single-layer) PS, CD, and ICS weekly networks.

**Update 4/28:** Pass/fail centrality plots started for PS. 

```{r packages, echo = FALSE}
library(igraph)
library(dplyr)
library(ggplot2)   # for boxplots
```

## Import data

At this point, `loadAllNetworks` and `calculatePR_TE_H` have already been run. Importing the results of that,

```{r}
(load("data/PRTEH.RData"))
```

There's a lot in there, but I'm mostly interested in the `accXX` objects, which hold the accumulated networks as of each week. 

```{r}
summary(accPS[[7]])
table(E(accPS[[7]])$weight)
```

Take a look at the pass/fail and just pass/just fail counts (these are the same in all three network layers):
```{r}
table(V(accPS[[7]])$pass, useNA = "ifany")
table(V(accPS[[7]])$justpass, useNA = "ifany")
nPass <- table(V(accPS[[7]])$pass, useNA = "ifany")
nJustPass <- table(V(accPS[[7]])$justpass, useNA = "ifany")
```


## Pass/fail boxplots

To do the pass/fail boxplots, I need a data frame with people's IDs, their pass/fail outcomes, and their centrality scores. I need this information for each week, with a column for week number as well. 

**TEMP HACK:** Need to avoid duplicate node names, so second "Person14" gets named "Person16
```{r, echo = FALSE}
for (i in seq(accPS)) {
  V(accPS[[i]])$name[15] <- "Person16"
  V(accCD[[i]])$name[15] <- "Person16"
  V(accICS[[i]])$name[15] <- "Person16"
}
```


```{r}
dfPS <- vector("list", length = length(accPS))
for (i in seq(dfPS)) {
  df <- igraph::as_data_frame(accPS[[i]], what = "vertices")
  df$Week <- i
  df$PageRank <- accPS_PR[[i]]$vector
  df$tarEnt <- accPS_TE[[i]]
  df$Hide <- accPS_H[[i]]
  
  dfPS[[i]] <- df %>% select(-id)  # ditch id column, it duplicates name + Person14 typo
}
dfPS <- bind_rows(dfPS)
dfPS <- subset(dfPS, select = c(Week, name:Hide))  # reorder to put Week first
# Need factors for plotting
dfPS$Week <- as.factor(dfPS$Week)   
dfPS$pass <- as.factor(dfPS$pass)
dfPS$justpass <- as.factor(dfPS$justpass)   
head(dfPS)
```

Now, I think, I can do the boxplots I need? For PageRank...

```{r}
ggplot(dfPS, aes(x = Week, y = PageRank)) + 
  geom_boxplot(aes(fill = pass)) + #theme(aspect.ratio = 4/7) +
  ggtitle(paste0("PS all passing/failing (",nPass[2],"/",nPass[1],")"))

dfPS %>% filter(is.na(justpass) == FALSE) %>% 
  ggplot(aes(x = Week, y = PageRank)) + 
  geom_boxplot(aes(fill = justpass)) + #theme(aspect.ratio = 4/7) +
  ggtitle(paste0("PS just passing/failing (",nJustPass[2],"/",nJustPass[1],")"))
```

The plot for all passing/failing looks pretty much the same as my old one. The justpass/justfail plot also looks similar, but seems to be missing some outlier points relative to the old plot. That's weird, since it has a few more data points in it. 

For Target Entropy:
```{r}
ggplot(dfPS, aes(x = Week, y = tarEnt)) + 
  geom_boxplot(aes(fill = pass)) + 
  ggtitle(paste0("PS all passing/failing (",nPass[2],"/",nPass[1],")"))

```

and for Hide:
```{r}
ggplot(dfPS, aes(x = Week, y = Hide)) + 
  geom_boxplot(aes(fill = pass)) + 
  ggtitle(paste0("PS all passing/failing (",nPass[2],"/",nPass[1],")"))
```

