---
title: "Logistic regression"
author: "Jesper Bruun & Adrienne Traxler"
date: "3/30/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Goal for this document is to make exploratory plots and run logistic regression for passing and failing in the (single-layer) PS, CD, and ICS weekly networks.

**Update 3/30:** Imported data and identified which objects I need. Do pass/fail centrality boxplots next. 

```{r packages, echo = FALSE}
library(igraph)
```

## Import data

At this point, `loadAllNetworks` and `calculatePR_TE_H` have already been run. Importing the results of that,

```{r}
(load("data/PRTEH.RData"))
```

There's a lot in there, but I'm mostly interested in the `accXX` objects, which hold the accumulated networks as of each week. 

```{r}
summary(accPS[[7]])
table(E(accPS[[7]])$weight)
```

Take a look at the pass/fail and just pass/just fail counts (these are the same in all three network layers):
```{r}
table(V(accPS[[7]])$pass, useNA = "ifany")
table(V(accPS[[7]])$justpass, useNA = "ifany")
```


## Pass/fail boxplots

DO THIS NEXT