---
title: "Centrality plots"
author: "Jesper Bruun & Adrienne Traxler"
date: "3/30/2020--5/8/2020"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Goal for this document is to make exploratory plots and run logistic regression for passing and failing in the (single-layer) PS, CD, and ICS weekly networks.

**Update 5/8:** Wrapping up centrality boxplots in its own file, and removing that from `logistic_regression.Rmd`. 

```{r packages, echo = FALSE}
library(igraph)
library(dplyr)
library(ggplot2)   # for boxplots
```

## Import data

At this point, `loadAllNetworks` and `calculatePR_TE_H` have already been run. **Update 5/8/20:** So has `make_node_data_frames.Rmd`. Importing the results of that gives me three long data frames. Each has all the node info (including centrality values), by week, for a single layer. 

```{r}
(load("../data/centrality_data_frames.Rdata"))
```

Check the contents:
```{r}
head(dfPS)
head(dfCD)
head(dfICS)
```



## Pass/fail boxplots

Now I can do the boxplots I need. For PageRank...

```{r}
ggplot(dfPS, aes(x = Week, y = PageRank)) + 
  geom_boxplot(aes(fill = pass)) + #theme(aspect.ratio = 4/7) +
  ggtitle(paste0("PS all passing/failing (",nPass[2],"/",nPass[1],")"))

dfPS %>% filter(is.na(justpass) == FALSE) %>% 
  ggplot(aes(x = Week, y = PageRank)) + 
  geom_boxplot(aes(fill = justpass)) + #theme(aspect.ratio = 4/7) +
  ggtitle(paste0("PS just passing/failing (",nJustPass[2],"/",nJustPass[1],")"))
```

The plot for all passing/failing looks pretty much the same as my old one. The justpass/justfail plot also looks similar, but seems to be missing some outlier points relative to the old plot. That's weird, since it has a few more data points in it. 

For Target Entropy:
```{r}
ggplot(dfPS, aes(x = Week, y = tarEnt)) + 
  geom_boxplot(aes(fill = pass)) + 
  ggtitle(paste0("PS all passing/failing (",nPass[2],"/",nPass[1],")"))

dfPS %>% filter(is.na(justpass) == FALSE) %>% 
  ggplot(aes(x = Week, y = tarEnt)) + 
  geom_boxplot(aes(fill = justpass)) + 
  ggtitle(paste0("PS just passing/failing (",nJustPass[2],"/",nJustPass[1],")"))
```

and for Hide:
```{r}
ggplot(dfPS, aes(x = Week, y = Hide)) + 
  geom_boxplot(aes(fill = pass)) + 
  ggtitle(paste0("PS all passing/failing (",nPass[2],"/",nPass[1],")"))

dfPS %>% filter(is.na(justpass) == FALSE) %>% 
  ggplot(aes(x = Week, y = Hide)) + 
  geom_boxplot(aes(fill = justpass)) + 
  ggtitle(paste0("PS just passing/failing (",nJustPass[2],"/",nJustPass[1],")"))
```

### Concept discussion layer

First PageRank:

```{r}
ggplot(dfCD, aes(x = Week, y = PageRank)) + 
  geom_boxplot(aes(fill = pass)) + 
  ggtitle(paste0("CD all passing/failing (",nPass[2],"/",nPass[1],")"))

dfCD %>% filter(is.na(justpass) == FALSE) %>% 
  ggplot(aes(x = Week, y = PageRank)) + 
  geom_boxplot(aes(fill = justpass)) + 
  ggtitle(paste0("CD just passing/failing (",nJustPass[2],"/",nJustPass[1],")"))
```

For Target Entropy:
```{r}
ggplot(dfCD, aes(x = Week, y = tarEnt)) + 
  geom_boxplot(aes(fill = pass)) + 
  ggtitle(paste0("CD all passing/failing (",nPass[2],"/",nPass[1],")"))

dfCD %>% filter(is.na(justpass) == FALSE) %>% 
  ggplot(aes(x = Week, y = tarEnt)) + 
  geom_boxplot(aes(fill = justpass)) + 
  ggtitle(paste0("CD just passing/failing (",nJustPass[2],"/",nJustPass[1],")"))
```

and for Hide:
```{r}
ggplot(dfCD, aes(x = Week, y = Hide)) + 
  geom_boxplot(aes(fill = pass)) + 
  ggtitle(paste0("CD all passing/failing (",nPass[2],"/",nPass[1],")"))

dfCD %>% filter(is.na(justpass) == FALSE) %>% 
  ggplot(aes(x = Week, y = Hide)) + 
  geom_boxplot(aes(fill = justpass)) + 
  ggtitle(paste0("CD just passing/failing (",nJustPass[2],"/",nJustPass[1],")"))
```


### In-class socializing layer

And the third set of boxplots. First PageRank:

```{r}
ggplot(dfICS, aes(x = Week, y = PageRank)) + 
  geom_boxplot(aes(fill = pass)) + 
  ggtitle(paste0("ICS all passing/failing (",nPass[2],"/",nPass[1],")"))

dfICS %>% filter(is.na(justpass) == FALSE) %>% 
  ggplot(aes(x = Week, y = PageRank)) + 
  geom_boxplot(aes(fill = justpass)) + 
  ggtitle(paste0("ICS just passing/failing (",nJustPass[2],"/",nJustPass[1],")"))
```

For Target Entropy:
```{r}
ggplot(dfICS, aes(x = Week, y = tarEnt)) + 
  geom_boxplot(aes(fill = pass)) + 
  ggtitle(paste0("ICS all passing/failing (",nPass[2],"/",nPass[1],")"))

dfICS %>% filter(is.na(justpass) == FALSE) %>% 
  ggplot(aes(x = Week, y = tarEnt)) + 
  geom_boxplot(aes(fill = justpass)) + 
  ggtitle(paste0("ICS just passing/failing (",nJustPass[2],"/",nJustPass[1],")"))
```

and for Hide:
```{r}
ggplot(dfICS, aes(x = Week, y = Hide)) + 
  geom_boxplot(aes(fill = pass)) + 
  ggtitle(paste0("ICS all passing/failing (",nPass[2],"/",nPass[1],")"))

dfICS %>% filter(is.na(justpass) == FALSE) %>% 
  ggplot(aes(x = Week, y = Hide)) + 
  geom_boxplot(aes(fill = justpass)) + 
  ggtitle(paste0("ICS just passing/failing (",nJustPass[2],"/",nJustPass[1],")"))
```

