---
title: "Cross-validation notes"
author: "Jesper Bruun & Adrienne Traxler"
date: "25 Jan 2021--"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Goal for this document is to summarize results from the cross-validation methods we used: Leave One Out Cross-Validation aka LOOCV aka jackknife, and k-fold cross-validation with `k=5` and `k=10`.

**Update 25 Jan:** Starting this file to document calculations I worked out in `passfail_XX_kfold.R` files. 

```{r packages, echo = FALSE, message = FALSE}
library(igraph)
library(tidyr)
library(dplyr)
library(ggplot2)
library(tibble)
```

## Import data

At this point, the following R scripts have already been run. 

* For LOOCV: `passfail_logreg_jackknife`, `passfail_lda_jackknife`, `passfail_qda_jackknife`, and `passfail_knn_jackknife`. 
* For k-fold cross-validation: `passfail_logreg_kfold`, `passfail_lda_lfold`, `passfail_qda_kfold` (ultimately not used, see notes below), and `passfail_knn_kfold`. 

Each of those files saves the predictions in an .Rdata file in the `data` directory and the success rate table in the `results` directory. Results are saved separately for the full set of pass/fail outcomes and for students who were just on the pass/fail border (the justpass outcome, saved in `Just` files). The k-fold results were saved for `k=5` and `k=10`. 

```{r}
filelist <- list.files(path = "../results", pattern = "*.csv")
infiles <- file.path("../results", filelist)
infiles 
allSuccRates <- lapply(infiles, read.csv) 
summary(allSuccRates)
```


### Clean up and organize

I want to name these appropriately and reorder them. Make sure each name is tagged with `pass` or `justpass` so I can use that below. 

```{r}
succLabels <- gsub("succRate", "", filelist) %>% 
  gsub(".csv", "", .) %>% 
  gsub("^_", "", .) %>% 
  paste0("pass.", .) %>% 
  gsub("^pass.Just_", "justpass.", .)
names(allSuccRates) <- succLabels
names(allSuccRates)

# Reorder to (logReg, LDA, QDA, KNN, (repeats for justpass))
newOrder <- c(8, 10, 9, 5, 7, 6, 11, 1, 3, 2)  
allSuccRates <- allSuccRates[c(newOrder, newOrder + 11)]
```

Now I'd like to put these into a long data frame so I can plot them more easily. In the process, I separate the `pass`/`justpass` label into its own column. 

```{r}
# see https://gist.github.com/aammd/9ae2f5cce9afd799bafb
succRateLong <- enframe(allSuccRates) %>% 
  unnest(cols = value) %>% 
  separate(col = name, into = c("outcome", "name"), sep = "[.]")
succRateLong
```

