---
title: "Logistic regression"
author: "Jesper Bruun & Adrienne Traxler"
date: "3/30/2020--"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Goal for this document is to run logistic regression for passing and failing in the (single-layer) PS, CD, and ICS weekly networks.

**Update 5/7:** Centrality boxplots finished, ready to update logistic regression results. 

```{r packages, echo = FALSE}
library(igraph)
library(dplyr)
```

## Import data

At this point, the following Rmd files have already been run: `loadAllNetworks`, `calculatePR_TE_H`, and `make_node_data_frames`. Importing the results of that gives me three long data frames. Each has all the node info and centrality values, by week, for a single layer. 

```{r}
(load("../data/centrality_data_frames.Rdata"))
```


## Logistic regression

As I recall, we had decided to skip the half-training, half-test approach because the data set isn't large enough to support that. If we stick with the "jackknife" approach, I can port in my old code.

The first thing I need is a list of data frames, rather than a single long data frame. Tidyverse to the rescue:

```{r}
centPS <- dfPS %>% group_split(Week)
centCD <- dfCD %>% group_split(Week)
centICS <- dfICS %>% group_split(Week)

centPS[[1]]
centPS[[2]]
```

Next, the function that actually does the calculations. 

* Input: A list of weekly data frames, optional outcome (pass/justpass, defaults to "pass"), and an optional subset of predictors to use (defaults gender, cohort, FCI pre, and centrality)
* Output: A data frame with node names, pass/fail outcome, and prediction vectors for that weekly aggregate network. Each node is predicted using all the other nodes in its week.

```{r}
jackPred <- function(layer, outcome = "pass", 
                     predictors = c("gender", "cohort", "fci_pre", "PageRank", 
                                    "tarEnt", "Hide")) {
  if (outcome == "pass" | outcome == "justpass") {
    choices <- c("0", "1")
  } else {
    stop("Not a valid outcome variable.")
  }
  # remove incomplete rows
  userows <- complete.cases(layer[[length(layer)]][, c(outcome,predictors)])  

  allprob <- matrix(nrow = sum(userows), ncol = length(layer))
  fitStr <- paste(predictors, collapse = " + ")
  fitForm <- paste0(outcome, " ~ ", fitStr)
  for(j in 1:length(layer)) {
    # data is complete cases
    data <- layer[[j]][userows, c(outcome, predictors)]
    # Loop through all nodes
    for(i in 1:dim(data)[1]) {
      # training set is data minus observation i
      train <- data[-i, ]
      glm.fit <- glm(fitForm, family = binomial, data = train)
      allprob[i, j] <- predict(glm.fit, newdata = data[i, ], type = "response")
    }
  }
  allpred <- allprob
  allpred[allprob < 0.5] <- choices[1]    # 0
  allpred[allprob >= 0.5] <- choices[2]   # 1
  
  # To return: node name, actual outcome, predicted outcome columns
  alldata <- data.frame(layer[[1]][userows, "name"], data[, outcome], as.data.frame(allpred))
  
  # Turn outcomes into factor
  for(i in seq_along(layer)) {
    alldata[, i+2] <- as.factor(alldata[, i+2])
  }
  
  names(alldata) <- c("name", outcome, paste0("Week", c(1:length(layer))))
  print(paste0("Fit: ", fitForm, ", complete N = ", dim(alldata)[1]))
  return(alldata)
}
```

It takes a few seconds to run the loop, so I'll import the results rather than executing it here.

```{r}
# Predict pass/fail
#predPS <- jackPred(centPS)
#predCD <- jackPred(centCD)
#predICS <- jackPred(centICS)

# Predict just-pass/just-fail (2/0)
#predJustPS <- jackPred(centPS, outcome = "justpass")
#predJustCD <- jackPred(centCD, outcome = "justpass")
#predJustICS <- jackPred(centICS, outcome = "justpass")

load("../data/jackknife_logistic_predictions.Rdata")
```

