---
title: "Logistic regression"
author: "Jesper Bruun & Adrienne Traxler"
date: "5/8/2020"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in Jesper's canonical network data and turn into node/centrality data frames. 

**Update 5/8:** 

```{r packages, echo = FALSE}
library(igraph)
library(dplyr)
library(ggplot2)   # for boxplots
```

## Import data

At this point, `loadAllNetworks` and `calculatePR_TE_H` have already been run. Importing the results of that,

```{r}
(load("../data/PRTEH.RData"))
```

There's a lot in there, but I'm mostly interested in the `accXX` objects, which hold the accumulated networks as of each week. 

```{r}
summary(accPS[[7]])
table(E(accPS[[7]])$weight)
```

Take a look at the pass/fail and just pass/just fail counts (these are the same in all three network layers):
```{r}
table(V(accPS[[7]])$pass, useNA = "ifany")
table(V(accPS[[7]])$justpass, useNA = "ifany")
nPass <- table(V(accPS[[7]])$pass, useNA = "ifany")
nJustPass <- table(V(accPS[[7]])$justpass, useNA = "ifany")
```


## Build data frames

To do pass/fail boxplots, logistic regression, and other analyses, I need a data frame with people's IDs, their pass/fail outcomes, and their centrality scores. I need this information for each week, with a column for week number as well. 

**TEMP HACK:** Need to avoid duplicate node names, so second "Person14" gets named "Person16
```{r, echo = FALSE}
for (i in seq(accPS)) {
  V(accPS[[i]])$name[15] <- "Person16"
  V(accCD[[i]])$name[15] <- "Person16"
  V(accICS[[i]])$name[15] <- "Person16"
}
```

Now I collect the node information into a long data frame. 

```{r}
# accNW should be one of accPS, accCD, or accICS
# accPR, accTE, and accH should be the corresponding centrality lists
make_node_df <- function(accNW, accPR, accTE, accH) {
  dflist <- vector("list", length = length(accNW))
  for (i in seq(dflist)) {
    df <- igraph::as_data_frame(accNW[[i]], what = "vertices")
    df$Week <- i
    df$PageRank <- accPR[[i]]$vector
    df$tarEnt <- accTE[[i]]
    df$Hide <- accH[[i]]
    
    dflist[[i]] <- df %>% select(-id)  # ditch id column, it duplicates name + Person14 typo
  }
  dfNW <- bind_rows(dflist)
  dfNW <- subset(dfNW, select = c(Week, name:Hide))  # reorder to put Week first
  
  # Need factors for plotting
  dfNW$Week <- as.factor(dfNW$Week)   
  dfNW$pass <- as.factor(dfNW$pass)
  dfNW$justpass <- as.factor(dfNW$justpass)   
  return(dfNW)
}
dfPS <- make_node_df(accPS, accPS_PR, accPS_TE, accPS_H)

head(dfPS)
```

Now concept discussion:

```{r}
dfCD <- make_node_df(accCD, accCD_PR, accCD_TE, accCD_H)
head(dfCD)
```

And in-class socializing:

```{r}
dfICS <- make_node_df(accICS, accICS_PR, accICS_TE, accICS_H)
head(dfICS)
```

There's some redundancy here--everything is the same except for the last three columns, which have the centrality values for that particular network layer. But rather than wrangling everything into a single data frame (and having to rewrite downstream code), I'm going to run with this for now. 

Save the output so I can use it in the next set of files:

```{r}
save(dfPS, dfCD, dfICS, nPass, nJustPass, file = "../data/centrality_data_frames.Rdata")
```

